|

### 2024-09-06 manuscript/paperCMSACversion.Rmd
fff
figure captions

```{r enforcer_density, echo = FALSE, fig.cap='Density Plot of Study Cohorts by DOB'}
#Note: I think the blue should be labeled as total players because it's stacked 
cohort_dat = dat %>% mutate(cohort = case_when(PIM.GP > 3 ~ 'Enforcer',
                                  #Total.Fights > 50 ~ 'Enforcer',
                                  .default = 'Non-Enforcer'))

@@

cohort_dat$cohort <- factor(cohort_dat$cohort, levels = c('Non-Enforcer', 'Enforcer'))

@@

\begin{table}
\begin{center}
\begin{tabular}{|c|c|}
\hline
 Variable & mean (sd)\\
 \hline
 n & `r nrow(dat)`    \\
 n deceased & `r sum(dat$dead)` (`r paste0(round(100*sum(dat$dead)/nrow(dat),2),"\\%")`)    \\
 Games Played & `r  round(mean(dat$GP.x),2)` (`r round(sd(dat$GP.x),2)`)\\
 Age (Years) & `r round(mean(as.numeric(dat$age)),2)` (`r round(sd(as.numeric(dat$age)),2)`)\\
 Height (Inches) & `r round(mean(as.numeric(dat$Ht)),2)` (`r round(sd(as.numeric(dat$Ht)),2)`)\\
 Weight (Pounds) & `r mean(as.numeric(dat$Wt))` (`r sd(as.numeric(dat$Wt))`)\\
 Fights per game & `r mean(as.numeric(dat$FperG))` (`r sd(as.numeric(dat$FperG))`)\\
 Penalty Minutes per game  & `r mean(as.numeric(dat$PIM.GP_numeric))`  (`r  sd(as.numeric(dat$PIM.GP_numeric))`)\\
 \hline
\end{tabular}
\end{center}
\caption{Overall summary stats
\label{tab:EDAoverall}}
\end{table}

@@

 \hline
\end{tabular}
\end{center}
\caption{Comparing enforcers to non-enforcers when enforcer is defined as E-F \label{tab:EDAEF}}
\end{table}

@@

\caption{Comparing enforcers to non-enforcers when enforcer is defined as E-P \label{tab:EDAEP}}
\end{table}

@@

```{r KMEF, echo = FALSE, fig.cap="Kaplan Meier plot for E-F" }
library(ggsurvfit)
survfit2(Surv ~ EFchar, data = dat) %>%
  ggsurvfit() +
  labs(
    x = "Age",
    y = "Overall survival probability"
  ) +
  add_confidence_interval()
```

```{r KMEP, echo = FALSE, fig.cap="Kaplan Meier plot for E-P" }
library(ggsurvfit)
survfit2(Surv ~ EPchar, data = dat) %>% 
  ggsurvfit() +
  labs(
    x = "Age",
    y = "Overall survival probability"
  ) + 
  add_confidence_interval()
```

@@

<!-- % latex table generated in R 4.2.2 by xtable 1.8-4 package -->
<!-- % Sep 4  2024 -->
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & $\beta$ & $e^{\beta}$ & s.e. & p-value \\ 
  \hline
  EFTRUE & 0.19994 & 1.22132 & 0.28948 & 0.48977 \\ 
  GP.x & -0.00061 & 0.99939 & 0.00023 & 0.00675 \\ 
  Ht & -0.03414 & 0.96644 & 0.04465 & 0.44455 \\ 
  Wt & 0.02134 & 1.02157 & 0.00658 & 0.00118 \\ 
  DOB.Year & -0.01691 & 0.98323 & 0.00825 & 0.04047 \\ 
  Pos2D & -0.38403 & 0.68111 & 0.17532 & 0.02849 \\ 
  Pos2W & -0.28394 & 0.75281 & 0.15967 & 0.07536 \\ 
   \hline
\end{tabular}
\caption{E-F \label{tab:EF}}
\end{table}

<!-- % latex table generated in R 4.2.2 by xtable 1.8-4 package -->
<!-- % Mon Feb 26 09:04:35 2024 -->
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & $\beta$ & $e^{\beta}$ & s.e. & p-value \\ 
  \hline
EPTRUE & 0.85436 & 2.34988 & 0.26474 & 0.00125 \\ 
  GP.x & -0.00052 & 0.99948 & 0.00022 & 0.01587 \\ 
  Ht & -0.02783 & 0.97255 & 0.04439 & 0.53069 \\ 
  Wt & 0.01859 & 1.01877 & 0.00659 & 0.00480 \\ 
  DOB.Year & -0.01699 & 0.98316 & 0.00831 & 0.04102 \\ 
  $I_D$ & -0.38847 & 0.67810 & 0.17549 & 0.02686 \\ 
  $I_W$ & -0.31332 & 0.73102 & 0.16048 & 0.05089 \\ 
   \hline
   \hline
\end{tabular}
\caption{E-P \label{tab:EP}}
\end{table}

>>>>

```{r enforcer_density, echo = FALSE, fig.cap='Proportion of Enforcer-Status Players to All Players by Date of Birth'}
#Note: I think the blue should be labeled as total players because it's stacked 
cohort_dat = dat %>% mutate(cohort = case_when(PIM.GP > 3 ~ 'Enforcer',
                                  #Total.Fights > 50 ~ 'Enforcer',
                                  .default = 'All Players'))

@@

cohort_dat$cohort <- factor(cohort_dat$cohort, levels = c('All Players', 'Enforcer'))

@@

\begin{table}
\begin{center}
\begin{tabular}{|c|c|}
\hline
 Variable & mean (sd)\\
 \hline
 n & `r nrow(dat)`    \\
 n deceased & `r sum(dat$dead)` (`r paste0(round(100*sum(dat$dead)/nrow(dat),2),"\\%")`)    \\
 Games Played & `r  round(mean(dat$GP.x),2)` (`r round(sd(dat$GP.x),2)`)\\
 Age (Years) & `r round(mean(as.numeric(dat$age)),2)` (`r round(sd(as.numeric(dat$age)),2)`)\\
 Height (Inches) & `r round(mean(as.numeric(dat$Ht)),2)` (`r round(sd(as.numeric(dat$Ht)),2)`)\\
 Weight (Pounds) & `r mean(as.numeric(dat$Wt))` (`r sd(as.numeric(dat$Wt))`)\\
 Fights per game & `r mean(as.numeric(dat$FperG))` (`r sd(as.numeric(dat$FperG))`)\\
 Penalty Minutes per game  & `r mean(as.numeric(dat$PIM.GP_numeric))`  (`r  sd(as.numeric(dat$PIM.GP_numeric))`)\\
 \hline
\end{tabular}
\end{center}
\caption{Descriptive Summary of All Hockey Players who Started after 1967 and Played at Least One Game Between the 1967-68 and 2022-2023 NHL seasons
\label{tab:EDAoverall}}
\end{table}

@@

 \hline
\end{tabular}
\end{center}
\caption{Comparison of Enforcers to Non-Enforcers when Enforcer is Defined by Career Fights (E-F) \label{tab:EDAEF}}
\end{table}

@@

\caption{Comparison of Enforcers to Non-Enforcers when Enforcer is Defined by Penalty Minutes (E-P) \label{tab:EDAEP}}
\end{table}

@@

```{r KMEF, echo = FALSE, fig.cap="Kaplan Meier Plot Comparing Survival Rates of Enforcers to Non-Enforcers when Enforcer is Defined by Career Fights (E-F)" }
library(ggsurvfit)
survfit2(Surv ~ EFchar, data = dat) %>%
  ggsurvfit() +
  labs(
    x = "Age",
    y = "Overall survival probability"
  ) +
  add_confidence_interval()
```

```{r KMEP, echo = FALSE, fig.cap="Kaplan Meier Plot Comparing Survival Rates of Enforcers to Non-Enforcers when Enforcer is Defined by Penalty Minutes (E-P)" }
library(ggsurvfit)
survfit2(Surv ~ EPchar, data = dat) %>% 
  ggsurvfit() +
  labs(
    x = "Age",
    y = "Overall survival probability"
  ) + 
  add_confidence_interval()
```

@@

<!-- % latex table generated in R 4.2.2 by xtable 1.8-4 package -->
<!-- % Sep 4  2024 -->
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & $\beta$ & $e^{\beta}$ & s.e. & p-value \\ 
  \hline
  EFTRUE & 0.19994 & 1.22132 & 0.28948 & 0.48977 \\ 
  GP.x & -0.00061 & 0.99939 & 0.00023 & 0.00675 \\ 
  Ht & -0.03414 & 0.96644 & 0.04465 & 0.44455 \\ 
  Wt & 0.02134 & 1.02157 & 0.00658 & 0.00118 \\ 
  DOB.Year & -0.01691 & 0.98323 & 0.00825 & 0.04047 \\ 
  Pos2D & -0.38403 & 0.68111 & 0.17532 & 0.02849 \\ 
  Pos2W & -0.28394 & 0.75281 & 0.15967 & 0.07536 \\ 
   \hline
\end{tabular}
\caption{Cox Proportional Hazards Model Output Comparing Enforcer to Non-Enforcer when Enforcer is Defined by Career Fights (E-F) and Controlling for Games
Played (GP), Height (Ht), Weight (Wt), Year of Birth (DOB), and Position Indicators \label{tab:EF}}
\end{table}

<!-- % latex table generated in R 4.2.2 by xtable 1.8-4 package -->
<!-- % Mon Feb 26 09:04:35 2024 -->
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & $\beta$ & $e^{\beta}$ & s.e. & p-value \\ 
  \hline
EPTRUE & 0.85436 & 2.34988 & 0.26474 & 0.00125 \\ 
  GP.x & -0.00052 & 0.99948 & 0.00022 & 0.01587 \\ 
  Ht & -0.02783 & 0.97255 & 0.04439 & 0.53069 \\ 
  Wt & 0.01859 & 1.01877 & 0.00659 & 0.00480 \\ 
  DOB.Year & -0.01699 & 0.98316 & 0.00831 & 0.04102 \\ 
  $I_D$ & -0.38847 & 0.67810 & 0.17549 & 0.02686 \\ 
  $I_W$ & -0.31332 & 0.73102 & 0.16048 & 0.05089 \\ 
   \hline
   \hline
\end{tabular}
\caption{Cox Proportional Hazards Model Output Comparing Enforcer to Non-Enforcer when Enforcer is Defined by Penalty Minutes (E-P) and Controlling for Games
Played (GP), Height (Ht), Weight (Wt), Year of Birth (DOB), and Position Indicators \label{tab:EP}}
\end{table}
